Croder: Bringing the Knowledge of the Crowds into the IDE

### 2013-05-03 paper/paper.tex
Integrated the work done for sketches
Issue #19

\section{Preliminary user study}
\section{Sketches}

>>>>

\section{Preliminary user study}

\section{Sketches}

Based on user interview study, we start to draw some initial sketches of workflow. At the beginning of 
drawing sketches, we focus on interface simplification. Many interviewee mentioned that it is a really 
hard time at the beginning of learning code specially for designers, architects or other students --
because they do not have any professional education background of computer science or coding. So 
based on simplification principle, we hide many features on main menu, make it more user-friendly and 
still have consistency and hierarchy between different features (see Figure~\ref{fig:sketches}).

\begin{figure}[hbt]
	\includegraphics[width=\columnwidth]{sketch1.jpg}
	\includegraphics[width=\columnwidth]{sketch2.jpg}
\caption{Initial design sketches}
\label{fig:sketches}
\end{figure}

After Showing these initial sketches to our interviewees, we got feedback about layout and interface 
graphic hierarchy. Based on these feedbacks, we developed a new interface for our program 
(Figure~\ref{fig:new interface}). Using metaphor method, the interface is like a hand-made leather 
cover notebook. This interface can recall user’s memory of using notebook to take note in class, in 
the meantime, make first time user specially user without background of coding quickly familiar with 
program.

\begin{figure}[hbt]
\begin{center}
	\includegraphics[width=0.8\columnwidth]{newinterface1.jpg}
	\includegraphics[width=0.8\columnwidth]{newinterface2.jpg}
	\includegraphics[width=0.8\columnwidth]{newinterface3.jpg}
	\includegraphics[width=0.8\columnwidth]{newinterface4.jpg}
\end{center}
\caption{Interface example}
\label{fig:newinterface}
\end{figure}
